---
title: "Webtoon Analysis"
author: "Bryce Wong"
date: "March 4, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(stringr)
library(tidyverse)
library(purrr)
```

## Exploratory analysis of the Webtoon Comment data

First reading in the data:

```{r reading in data}
webtoons_data = read_csv(file = "./data/comments.csv")

webtoons_data = webtoons_data %>% 
  select(-X1)
```

Now getting the number of comments per each episode:

* Outputting table of top 10 episodes by number of comments

```{r}
#number of comments per each episode
num_eps = webtoons_data %>%
  count(episode) %>% 
  arrange(desc(n))

#outputting table of top 10 episodes by number of comments
num_eps %>% 
  top_n(10) %>% 
  rename(number_of_comments = n) %>% 
  knitr::kable(digits = 3)
```

Now getting the number of likes per each comment:

* Outputting table of top 10 comments by number of likes

```{r}
#arranging comments by likes
arrange_by_likes = webtoons_data %>%
  arrange(desc(likes)) 

#outputting table of top 10 comments by number of likes
head(arrange(webtoons_data, desc(likes)), 10) %>% 
  knitr::kable(digits = 3)
```

Now getting the number of comments per each unique user:

* Outputting table of top 10 users by number of comments

```{r}
#number of comments each unique user has posted
num_users = webtoons_data %>%
  count(username) %>% 
  arrange(desc(n)) 

#outputting table of top 10 users by number of comments
num_users %>% 
  top_n(10) %>% 
  rename(number_of_comments = n) %>% 
  knitr::kable(digits = 3)
```
  
Now a bunch of tables showing basic summary statistics for:

* comments across all episodes
* comments across all users
* likes across all comments

Also, one histogram at the end to show the distribution of likes.

(The histogram of the distribution of number of comments per episode was a bit funky and probably not worth viewing)

```{r}
#stats of comments across all episodes
avg_num_comm = num_eps %>%
  summarize(mean_comments_per_ep = mean(n),
            median_comments_per_ep = median(n),
            sd_comments = sd(n)) %>% 
  knitr::kable(digits = 3)

avg_num_comm

#stats of commentators
avg_user = num_users %>%
  summarize(mean_comments_per_user = mean(n),
            median_comments_per_user = median(n),
            sd_comments = sd(n)) %>% 
  knitr::kable(digits = 3)

avg_user

#stats of likes
avg_likes = webtoons_data %>%
  summarize(mean_likes_per_comment = mean(likes),
            median_likes_per_comment = median(likes),
            sd_likes = sd(likes)) %>% 
  knitr::kable(digits = 3)

avg_likes

#visualizations

#distribution of likes
ggplot(webtoons_data, aes(x = likes)) + 
  geom_histogram() + 
  labs(
    title = "Distribution of likes per comment",
    x = "Number of likes",
    y = "Count"
  )
```
